Fig2

### 2020-02-21 analysis/figure-2.Rmd
now with allDEGs file

```{r}
allDEG %>%
  group_by(tissue, comparison) %>%
  summarize(totalDEGs = n()) %>%
  arrange(tissue, comparison)
```

@@

write_csv(table1, "../results/table1.csv")
```

>>>>

```{r}
allDEG %>%
  group_by(sex, tissue, comparison) %>%
  summarize(totalDEGs = n()) %>%
  arrange(tissue, comparison)
```

@@

write_csv(table1, "../results/table1.csv")

suppletable1 <- allDEG %>%
  filter(comparison != "control_bldg") %>%
  group_by(sex, tissue, comparison) %>%
  arrange( tissue, sex)

suppletable1 %>%
  group_by(tissue) %>%
  summarize(totalDEGs = n())

write_csv(table1, "../results/suppletable1.csv")
